\documentclass[../main.tex]{subfiles}

%%%%%
% The word ACKNOWLEDGEMENTS be 14 pt font 
% \fontsize{14}{16} \selectfont
% The body must be in 12 pt font
% \fontsize{12}{14} \selectfont
% No indentations between paragraphs
%%%%%

\begin{document}
\begin{center}
\fontsize{14}{16.8} \selectfont{ACKNOWLEDGEMENTS}
\end{center}

\begin{singlespace}
\fontsize{12}{14} \selectfont{

{\parindent0pt % disables indentation for all the text between { and }
%\begin{flushleft}
                                                                                 
This thesis was made possible by the many extraordinary people in my life. Words are insufficient to express my gratitude to all of you. \\

%\end{flushleft}
} % end of no indent

{\parindent0pt % disables indentation for all the text between { and }
%\begin{flushleft}

Thank you to my advisor, Todd Averett, for his constant support and guidance. I am extremely grateful for the freedom and independence you allowed me in my work. The free reign you gave me at Jefferson Lab let me experience every part of planning, building, running, and analyzing experiments. \\

%\end{flushleft}
} % end of no indent

{\parindent0pt % disables indentation for all the text between { and }
%\begin{flushleft}
                                                                                 
I would also like to thank my Jefferson Lab advisor, Douglas Higinbotham. You had no obligation to give me your time, yet you chose to become a mentor. In doing so, you gave me countless hours of advice and guidance. Your passion and enthusiasm for physics was a steady reminder of why we do our research. You kept advocating for my part of the Tritium Experiments, and though it never happened you provided me with the data used in this thesis making thesis plan number three the final one. \\

%\end{flushleft}
} % end of no indent

{\parindent0pt % disables indentation for all the text between { and }
%\begin{flushleft}
                                                                                 
My thanks to the many others at Jefferson Lab who supported me in my graduate work. I am grateful to my other Jefferson Lab mentors, Bogdan Wojtsekhowski and Bob Michaels, for patiently lending me their time and expertise as I learned the work of a physics researcher. Thanks to all of the fellow graduate students I worked with over the years, particularly those in the Tritium Collaboration. I offer a special thank you to, Dien Nguyen, for pioneering this dataset and helping me with the initial analysis. Thanks also to the many postdocs I have worked with including Carlos Ayerbe-Gayoso, Huan Yao, Evan McClellan, and Florian Hauenstein for their willingness to teach me.\\

%\end{flushleft}
} % end of no indent

{\parindent0pt % disables indentation for all the text between { and }
%\begin{flushleft}
                                                                                 
Thanks as well to Eugene Tracy and Seth Aubin, along with the other members of the Climate Steering Committee and the Diversity Advisory Committee. These committees provided me a constructive outlet and source of comfort in dark times. While our are efforts are just the beginning, and will likely never truly end, the department is better for all of your hard work.\\

%\end{flushleft}
} % end of no indent

{\parindent0pt % disables indentation for all the text between { and }
%\begin{flushleft}
                                                                                 
Thank you to the staff working behind the scenes to make the physics department tick. The dedication to the department and students shown by Paula Perry, Eleonor Wilkinson, Carolyn Hankins, and Bonnie Willard makes our journey from orientation to graduation as smooth and well-organized as possible. \\

%\end{flushleft}
} % end of no indent

{\parindent0pt % disables indentation for all the text between { and }
%\begin{flushleft}
                                                                                 
Too many people have contributed along my educational journey to list, but a few teachers made particularly large impacts on my life and education. At W$\&$M this includes Seth Aubin and Chris Carone for their outstanding teaching abilities. At Drake my professors Athanasios Petridis and Charles Nelson were excellent teachers as well, and Dr. Petridis recommended W$\&$M and Jefferson Lab to me. In high school my teachers Dan Butler, Gretchen Nesset, Graham Wright, and Cheryl Wason were phenomenal teachers in academics and life. I would also like to thank my elementary school science teacher John `Jack' Briggs for sparking my interest in science with the star lab and crayfish labs as well as Margot Brooks, Fran Buesgens, and Ms. Bell. \\

%\end{flushleft}
} % end of no indent

{\parindent0pt % disables indentation for all the text between { and }
%\begin{flushleft}
                                                                                 
Of course, none of this would be possible without the love and support of my family. Thank you to my parents, Kevin and Vicki Barcus, for giving me every possible advantage in life. Thank you for encouraging me to follow my own path in life and for cheering me on at every turn. You raised me to be the person I am happy to be today. I will always be proud to return your unconditional love. Thanks to my brother, Jeff Barcus, who has always been a kindred spirit and someone I can be completely open with. I will always cherish your companionship. Thanks also to my grandparents Nancy and Roger Johnson and Colleen and Wayne Barcus as well as my extended family for their love. I look forward to being back for more fishing trips and croquet games in the future.\\

%\end{flushleft}
} % end of no indent

{\parindent0pt % disables indentation for all the text between { and }
%\begin{flushleft}
                                                                                 
I must also thank the many friends I made a W$\&$M. Without their help, passing my classes and completing this program would have been infinitely more difficult. To Matthew `Perry' Nerem, our racquetball games and `bro nights' are always a highlight of my week, and your friendship means the world to me. To Aria Johansen, you showed me how to live a strong life and opened my mind to a world of new possibilities. Your friendship taught me more about myself than anyone else has, and it will always be treasured. To Kurtis Bartlett, I have met none as steadfast, loyal, and principled as you. I do not have the room to tell you all how much you mean to me, but to Daniel Salmon, Carlie Crawford, Douglas Beringer, Melissa Beebe, Anashe Bandari, Marco Colo, Denise McKaig, and the others I met along the way thank you for your friendship. Few times were as happy as our board game days.\\

%\end{flushleft}
} % end of no indent

{\parindent0pt % disables indentation for all the text between { and }
%\begin{flushleft}
                                                                                 
Finally, while I consider many of those above to be family, I want to thank my first chosen family as well. To Nathaniel Severson, since that first day we rode Big Wheels together your friendship has always been a source of joy for me. To Handi Xue, your decision that we would be friends in middle school was the best decision ever made for me. Growing up with the two of you formed me into the person I am today, and I am forever grateful for your friendship. To Evan Shapiro, you went from a randomly assigned roommate to a lifelong friend in almost no time at all. Ever since our late night dorm room chats you have always inspired me to better myself. To Forrest Williams, I can always count on you to laugh at a terrible joke, and I am so thankful for the ear you are always willing to lend when things get rough. Never have I had a friend more eager to pour their considerable energy into making the most of their friendships. To John Message, my first chosen roommate, I will always treasure the time we spent on the couch with me yelling at the news and you tolerating this in companionable silence. You taught me so much about being an adult and were instrumental in broadening my somewhat limited horizons. To Nicholas Dorando, my other chosen roommate, you imbue everyone around you with your unbridled enthusiasm for life and all of its joys. You make me and the world better by showing how one lives a life full of empathy and kindness. Thank you all for being there for me through the good and the bad, especially when I was probably a lot less fun to be around. Whether it is called the Aquarium, the Aviary, or the Apiary our regular calls have kept me sane throughout this process, and they give me a great sense of comfort knowing that I will never be alone going forward.\\

%\end{flushleft}
} % end of no indent

{\parindent0pt % disables indentation for all the text between { and }
%\begin{flushleft}
                                                                                 
Thank you all!                                                     

%\end{flushleft}
} % end of no indent

} % end of font size 12
\end{singlespace}

\end{document}